Analysis Stand Features 

### 2017-05-16 analysis/analysis_stand_features.Rmd
update analysis; +create csv with tables

>>>>

```{r}
# Join all data and export as table

# Get name of variables 
variables <- compe %>% dplyr::select(ba:dnn) %>% names() %>% rbind()
# Add topo and focal tree variables 
nombres <- c(variables, 'mde','slope', 'dn', 'h')

out <- c()

for (i in nombres){ 
  # name of aov object
  aov_name <- paste0('aov_',i)
  # get aov_object 
  aux <- get(aov_name)
  # get summ comparison dataframe 
  aux2 <- aux$summ_comparison
  out <- rbind(out, aux2)
}

out2 <- out %>% dplyr::select(site, mean, sd, tukey, mivar = variable)

# See this solution 
# http://stackoverflow.com/questions/39066811/long-to-wide-with-dplyr
# http://garrettgman.github.io/tidying/
out3 <- gather(out2, variable, value, mean, sd, tukey) %>% 
  unite(var, variable, site) %>% 
  spread(var, value, convert=TRUE)

out4 <- out3 %>% 
  transmute(variables = mivar,
            CA_High_m = round(mean_CA_High, 3),
            CA_High_sd = round(sd_CA_High, 3),
            CA_High_l = tukey_CA_High,
            CA_Low_m = round(mean_CA_Low, 3),
            CA_Low_sd = round(sd_CA_Low, 3),
            CA_Low_l = tukey_CA_Low,
            SJ_High_m = round(mean_SJ_High, 3),
            SJ_High_sd = round(sd_SJ_High, 3),
            SJ_High_l = tukey_SJ_High,
            SJ_Low_m = round(mean_SJ_Low, 3),
            SJ_Low_sd = round(sd_SJ_Low, 3),
            SJ_Low_l = tukey_SJ_Low)

# Export data 
write.csv(out4, file=paste(di, "data/proto_tables/site_features.csv", sep=""), row.names = FALSE)

## General Variables and coordinates

general_var %>% 
  left_join(coords_sites, by='site') %>% 
  write.csv(file=paste(di, "data/proto_tables/site_general.csv", sep=""), row.names = FALSE)
```
